Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
Rewording the LB (still follows the Mahmoud's construction)

	Then, we join the pivot node to a~larger ground set to force its eviction.
	Precisely,
	we create a~ground set $\{x_0, y_0\}$, 	where
%	 $x_0$ is the current pivot node and
	 $y_0$ is an arbitrary isolated node.
	Since \ALG does not have $\{x_0,y_0\}$ collocated, 
	we issue an external request between them so that \ALG collocates them.
	\ALG cannot collocate $\{x_0, y_0\}$ with $B$ (as $B$'s size is $k-1$), hence it collocates them in a different cluster.
	In order to preserve a~feasible partition of nodes after collocating $\{x_0, y_0\}$,
	\ALG must replace $x_0$ with another isolated node.
%	denoted by $x_1$.

	We proceed by joining the current pivot node to a~larger ground set in a similar way,
	as long as a feasible partition exists afterward.
	Consider the isolated node $x_i$ currently collocated with $B$.
	 We issue a request between $x_i$ and some node $y_i \in C_i$,
	 where $C_i$ is the largest ground set
	 s.t.~$I(C_i) = I(x_i), C_i \neq \{x_0,y_0\}$,
	 only if  a feasible partition exists
	 that collocates all nodes in $\{x_i\} \cup C_i $.
	Any such feasible partition replaces $x_i$ with some isolated node $x_{i+1}$,
	as the new ground set $\{x_i\} \cup C_i $  may not be ever split.
	Otherwise,
	no such feasible partition exists and
	we terminate the process.

@@

	The number of isolated nodes decrease after each step.
	Consider the last step, $j$, when exactly $\ell+1$ isolated nodes exist before  $x_{j}$ joins to another ground set.
	That is, there are less than $\ell+1$ isolated nodes after the step $j$.
	Then, at the end of step $j-1$,
	there exist two isolated nodes $x^*$ and $y^*$
	with the same cluster of origin, i.e., $I(\{x^*\})=I(\{y^*\})$.
%
   Next,
    we bound costs incurred by \OPT and \ALG over the  sequence of requests
    $\sigma := \langle \{x_0,y_0\}, \dots, \{x_{j-1},y_{j-1}\}  \rangle$.

>>>>

	Then, we join the pivot node to a~larger ground set to force its eviction.
	Precisely,
	we create a~ground set $\{x_0, y_0\}$, 	where
%	 $x_0$ is the current pivot node and
	 $y_0$ is an arbitrary isolated node.
	Since \ALG does not have $\{x_0,y_0\}$ collocated, 
	the adversary issues external requests to this pair until \ALG collocates it.
	\ALG cannot collocate $\{x_0, y_0\}$ with $B$ (as $B$'s size is $k-1$), hence it collocates them in a~different cluster.
	In order to preserve a~feasible partition of nodes after collocating $\{x_0, y_0\}$,
	\ALG must replace $x_0$ with another isolated node that becomes the new pivot.
%	denoted by $x_1$.

	We proceed by joining the current pivot node to a~larger ground set in a similar way, as long as a feasible partition of ground sets exists after the join.
	In a single step, we merge the ground sets of the current pivot $x_i$ and the largest ground set $C$ s.t. $C \neq \{x_0,y_0\}$ and $I(C) = I(x_i)$.
	This forces \ALG to collocate $\{x_i\} \cup C_i $ and to replace $x_i$ with some isolated node $x_{i+1}$.
	(Note that these ground sets contain nodes that originate from the same cluster, whereas the nodes $x_0$ and $y_0$ originate from distinct clusters.)

@@

	The number of isolated nodes decreases after each step.
	Consider the last step, $j$, when exactly $\ell+1$ isolated nodes exist before  $x_{j}$ joins to another ground set.
	That is, there are less than $\ell+1$ isolated nodes after the step $j$.
	Then, at the end of step $j-1$,
	there exist two isolated nodes $x^*$ and $y^*$
	with the same cluster of origin, i.e., $I(\{x^*\})=I(\{y^*\})$.
%
   Next,
    we bound costs incurred by \OPT and \ALG over the  sequence of requests
    $\sigma := \langle \{x_0,y_0\}, \dots, \{x_{j-1},y_{j-1}\}  \rangle$.
